Simulated Observations of Young Protoplanetary Discs

### 2013-01-21 paper.tex
authors corrected and a few minor fig changes

\documentclass[useAMS,usenatbib]{mn2e}
\usepackage{graphicx}
\usepackage{float}

@@

\title[Young protoplanetary discs]{Simulated observations of young protoplanetary discs}
%authors arent splitting over 2 lines so rawlings is pushed off the edge
\author[Tom Douglas, Paola Caselli, Et al.]{Tom Douglas$^{1}$\thanks{E-mail:
pytd@leeds.ac.uk}, Paola Caselli$^{1}$, Aaron Boley$^{2}$, Richard Durisen$^{3}$, Tom Hartquist$^{1}$, John Ilee$^{1}$, Jonathon Rawlings$^{4}$ \\
$^{1}$School of Physics and Astronomy, University of Leeds, Leeds LS2 9JT, UK \\
$^{2}$Department of Astronomy, University of Florida, 211 Bryant Space Center, PO Box 112055, USA\\
$^{3}$Department of Astronomy, Indiana University, 727 East 3rd Street, Swain West 319, Bloomington, IN 47405, USA\\
%$^{4}$Department of Physics & Astronomy, University College London, London WC1E 6BT, UK\\
}
\begin{document}

\date{In original form 2012}

@@

\begin{figure*}
 \includegraphics[width=168mm]{Figures/model/rhoT2.eps}
 \label{rhoT} 
 \caption{{\bf Left:} A 3D plot of log number density (cm$^{-3}$) showing the spiral structure in the xy plane and scale height of the disc. {\bf Right:} The 3D temperature structure of the disc; regions cooler than 40 degrees are not shown in 3D, demonstrating the narrow central region containing hot material.}
\end{figure*}

@@

\begin{figure*}
 \includegraphics[width=168mm]{Figures/sim/channel_map-1.eps} 
 \label{h2co_chanmap}
 \caption{H$_2$CO 4$_{04}$-3$_{03}$ channel maps as simulated by CASA. H$_2$CO line in contours starting at 0.35 mJy$\,$beam$^{-1}\,$km$\,$s$^{-1}$ (absorption in red, emission in blue). Overlaid on the continuum emission. Each map integrates over 2.4 km$\,$s$^{-1}$ with the top left from -10.8 to -8.4 km$\,$s$^{-1}$ to the bottom left ranging from 8.4 to 10.8 km$\,$s$^{-1}$}
\end{figure*}

>>>>

\documentclass[useAMS,usenatbib]{mn2e}
\usepackage{graphicx}
\usepackage{float}
\usepackage{wasysym}
\usepackage{stmaryrd}
\usepackage{txfonts}
\usepackage{natbib}
\usepackage{color}
\usepackage{colortbl}
\usepackage{multirow}

% Journal Definitions
\def   \aj {{\rm {AJ}}}
\def   \araa {{\rm {ARA\&A}}}
\def   \apj {{\rm {ApJ}}}
\def   \icarus {{\rm {Icarus}}}
\def   \apjs {{\rm {ApJS}}}
\def   \apss {{\rm {Ap\&SS}}}
\def   \aap {{\rm {A\&A}}}
\def   \aapr {{\rm {A\&AR}}}
\def   \aaps {{\rm {A\&AS}}}
\def   \baas {{\rm {BAAS}}}
\def   \memras {{\rm {MmRAS}}}
\def   \mnras {{\rm {MNRAS}}}
\def   \prl {{\rm {Phys. Rev. Lett.}}}
\def   \jqsrt {{\rm {Journal of Quantitative Spectroscopy and Radiative Transfer}}}
\def   \apjl{\rm {ApJL}}
\def   \nat{\rm {Nat.}}

@@

\title[Young protoplanetary discs]{Simulated Observations of Young Protoplanetary Discs}
%%authors arent splitting over 2 lines so rawlings is pushed off the edge
%\author[Tom Douglas, Paola Caselli, Et al.]{Tom Douglas$^{1}$\thanks{E-mail:
%pytd@leeds.ac.uk}, Paola Caselli$^{1}$, Aaron Boley$^{2}$, Richard Durisen$^{3}$, Tom Hartquist$^{1}$, %John Ilee$^{1}$, Jonathon Rawlings$^{4}$ \\
%$^{1}$School of Physics and Astronomy, University of Leeds, Leeds LS2 9JT, UK \\
%$^{2}$Department of Astronomy, University of Florida, 211 Bryant Space Center, PO Box 112055, USA\\
%$^{3}$Department of Astronomy, Indiana University, 727 East 3rd Street, Swain West 319, Bloomington, IN %47405, USA\\
%%$^{4}$Department of Physics & Astronomy, University College London, London WC1E 6BT, UK\\
%}

\author[T.~A.~Douglas et al.]
{\parbox{\textwidth}{Tom Douglas$^{1}$\thanks{E-mail: \texttt{pytd@leeds.ac.uk}},
Paola Caselli$^{1}$,
Aaron Boley$^{2}$,
Richard Durisen$^{3}$,
Tom Hartquist$^{1}$,
John Ilee$^{1}$ and
Jonathon Rawlings$^{4}$\\
\vspace{0.1cm}\\
{\small{\it$^{1}$School of Physics and Astronomy, University of Leeds, Leeds LS2 9JT, UK}} \\
{\small{\it$^{2}$Department of Astronomy, University of Florida, 211 Bryant Space Center, PO Box 112055, USA}}\\
{\small{\it$^{3}$Department of Astronomy, Indiana University, 727 East 3rd Street, Swain West 319, Bloomington, IN 47405, USA}}\\
{\small{\it$^{4}$Department of Physics \& Astronomy, University College London, London WC1E 6BT, UK}}\\}}

%{\parbox{\textwidth}{
%$^{1}$School of Physics and Astronomy, University of Leeds, Leeds LS2 9JT, UK \\
%$^{2}$Department of Astronomy, University of Florida, 211 Bryant Space Center, PO Box 112055, USA\\
%$^{3}$Department of Astronomy, Indiana University, 727 East 3rd Street, Swain West 319, Bloomington, IN %47405, USA\\
%$^{4}$Department of Physics & Astronomy, University College London, London WC1E 6BT, UK\\
%}}

\begin{document}

\date{In original form 2013}

@@

\begin{figure*}
 \includegraphics[width=168mm]{Figures/model/rhoT6.eps}
 \label{rhoT} 
 \caption{{\bf Left:} A 3D plot of log number density (cm$^{-3}$) showing the spiral structure in the xy plane and scale height of the disc. {\bf Right:} The 3D temperature structure of the disc; regions cooler than 40 degrees are not shown in 3D, demonstrating the narrow central region containing hot material.}
\end{figure*}

@@

\begin{figure*}
 \includegraphics[width=168mm]{Figures/sim/channel_map-1.eps} 
 \label{h2co_chanmap}
 \caption{H$_2$CO 4$_{04}$-3$_{03}$ channel maps as simulated by CASA. H$_2$CO line in contours starting at 0.35 mJy$\,$beam$^{-1}\,$km$\,$s$^{-1}$ (absorption in blue, emission in red). Overlaid on the continuum emission. Each map integrates over 2.4 km$\,$s$^{-1}$ with the top left from -10.8 to -8.4 km$\,$s$^{-1}$ to the bottom left ranging from 8.4 to 10.8 km$\,$s$^{-1}$}
\end{figure*}
